Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-02-06 paper.qmd
Updated Measutring fit

The model here is similar to a confirmatory factor analysis model [@brown2015], $\widehat{T}(X_1, X_2, X_3) + \Epsilon$. The difference between the fitted model and observed values would be considered to be residuals, and for this problem are $7\text{-}D$.

>>>>

The model here is similar to a confirmatory factor analysis model [@brown2015], $\widehat{T}(X_1, X_2, X_3, X_4) + \Epsilon$. The difference between the fitted model and observed values would be considered to be residuals, and for this problem are $4\text{-}D$.
